Share Buyback and Equity Issue Anomalies Revisited

### 2016-02-25 index.Rmd
updates

```{r, fig.width=6, fig.height=5,echo=FALSE}
downloadHandler(
  filename = "report.pdf",
  content = function(file) {
    knitr::knit2pdf("report.Rnw",envir=environment())
    file.rename(normalizePath('report.pdf'), file)
  }
)
```

@@

feature_IRATStable_industry <- reactive({
  useonly_industry = !(DATASET_NEW()$SDC$Industry %in% input$industry) 
  res = round(cbind(
    #car_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], DATASET_NEW()$SDC$Event.Date[useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], Risk_Factors_Monthly)$results,
    #car_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued], DATASET_NEW()$SDC$Event.Date[useonly_industry& DATASET_NEW()$SDC$company_subset_undervalued], Risk_Factors_Monthly)$results
    car_table_cached(DATASET_NEW()$CACHE,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued)$results,
    car_table_cached(DATASET_NEW()$CACHE,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  as.data.frame(res)
})

>>>>

```{r, fig.width=6, fig.height=5,echo=FALSE}
downloadHandler(
  filename = "report.pdf",
  content = function(file) {
    tosave= list("startdate","enddate","market_cap_min","market_cap_max","quantile_used_ind","quantile_used_all","characteristic_irats1","characteristic_irats2","characteristic_irats3","characteristic_irats4","characteristic_irats5","characteristic_irats6","characteristic_irats1_sign","characteristic_irats2_sign","characteristic_irats3_sign","characteristic_irats4_sign","characteristic_irats5_sign","characteristic_irats6_sign")
    newinput <- list()
    for(i in tosave) {
      newinput[[i]] <- input[[i]]
    }

    save("newinput",file=normalizePath("input.Rdata"))
    knitr::knit2pdf("report.Rnw",envir=globalenv())
    file.rename(normalizePath('report.pdf'), file)
  }
)
```

@@

feature_IRATStable_industry <- reactive({
  useonly_industry = !(DATASET_NEW()$SDC$Industry %in% input$industry) 
  cat(paste("Total left after filtering industry:",sum(useonly_industry)))
  res = round(cbind(
    #car_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], DATASET_NEW()$SDC$Event.Date[useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued], Risk_Factors_Monthly)$results,
    #car_table(DATASET_NEW()$returns_by_event_monthly[,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued], DATASET_NEW()$SDC$Event.Date[useonly_industry& DATASET_NEW()$SDC$company_subset_undervalued], Risk_Factors_Monthly)$results
    car_table_cached(DATASET_NEW()$CACHE,useonly_industry & DATASET_NEW()$SDC$company_subset_overvalued)$results,
    car_table_cached(DATASET_NEW()$CACHE,useonly_industry & DATASET_NEW()$SDC$company_subset_undervalued)$results
  ),2)[reported_times,]
  colnames(res) <- c("Low: CAR", "t-stat","p-value", "High: CAR", "t-stat","p-value")
  as.data.frame(res)
})

### 2016-02-25 report.Rnw
updates

source("lib_helpers.R",local=environment())
source("latex_code.R",local=environment())
source("dataset/indices_and_factors/ff_industries_sic.R",local=environment())
source("business_data_clean.R",local=environment())
source("Paper_global_parameters.R",local=environment())

@@

#Add any/all choices made in the tool here
if(!exists("input") ){#& FALSE
  input = list()
  input$startdate <- as.Date("1984-12-31")
  input$enddate <- as.Date("2014-12-31")
  market_cap_min = "10"
  market_cap_max = "10000"
  quantile_used_ind = "0.2"
  quantile_used_all = "0.4"

  #for extra sections
  input$characteristic_irats1 <- "BE.ME.Score"
  input$characteristic_irats1_sign <- T

  input$characteristic_irats2 <- "pre.vol.Score"
  input$characteristic_irats2_sign <- T
}
market_cap_min = as.numeric(input$market_cap_min)
market_cap_max = as.numeric(input$market_cap_max)
quantile_used_ind = as.numeric(input$quantile_used_ind)
quantile_used_all = as.numeric(input$quantile_used_all)

@@

#Now overwrite any variables that need redefining
firstyear = as.character(format(input$startdate,"%Y"))
lastyear = as.character(format(input$enddate,"%Y"))
FirstTrade = input$startdate

@@

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
SEO_exit_days = sapply(which(BUYBACK_DATA_NEW$DATASET$SDC$Otherlater != "2100-01-01"), function(i) as.Date(BUYBACK_DATA_NEW$DATASET$SDC$Otherlater[i]) - event.date_bb[i])
BB_exit_days = sapply(which(ISSUERS_DATA$DATASET$SDC$Otherlater != "2100-01-01"), function(i) as.Date(ISSUERS_DATA$DATASET$SDC$Otherlater[i]) - event.date_iss[i])
@

>>>>

options(warn=-1) #because some packages give warnings
source("lib_helpers.R",local=environment())
source("latex_code.R",local=environment())
source("dataset/indices_and_factors/ff_industries_sic.R",local=environment())
source("business_data_clean.R",local=environment())
source("Paper_global_parameters.R",local=environment())
options(warn=0)

@@

#Add any/all choices made in the tool here
if(!exists("input") ){#& FALSE
  load(normalizePath("input.Rdata")) #this is updated by the Rmd
  input <- newinput
}
market_cap_min = as.numeric(input$market_cap_min)
market_cap_max = as.numeric(input$market_cap_max)
quantile_used_ind = as.numeric(input$quantile_used_ind)
quantile_used_all = as.numeric(input$quantile_used_all)

@@

#Now overwrite any variables that need redefining
firstyear = as.character(format(input$startdate,"%Y"))
lastyear = as.character(format(input$enddate,"%Y"))
FirstTrade = input$startdate
@

@@

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
SEO_exit_days = sapply(which(BUYBACK_DATA_NEW$DATASET$SDC$Otherlater != "2100-01-01"), function(i) as.Date(BUYBACK_DATA_NEW$DATASET$SDC$Otherlater[i]) - event.date_bb[i])
BB_exit_days = sapply(which(ISSUERS_DATA$DATASET$SDC$Otherlater != "2100-01-01"), function(i) as.Date(ISSUERS_DATA$DATASET$SDC$Otherlater[i]) - event.date_iss[i])

SEO_exit_days = ifelse(is.null(SEO_exit_days),list(),SEO_exit_days)
BB_exit_days = ifelse(is.null(BB_exit_days),list(),BB_exit_days)
@
